\section{Methodology}\label{sec:method}

The primary objective of our study was to critically study the e-Passport portal application from a Software Engineering and System Design point of view. The applied methodology was to test every feature of the website by hand, and report any issues found related to the user interface, technical performance, and informational clarity. Aside from using and testing it ourselves, we collected public opinions on the existing application through a carefully curated anonymous questionnaire survey distributed through public social media platforms. Hence, the analysis of our chosen application heavily relies on both personal and popular use-case scenarios and first-hand user experience. The goal of the experiment was to figure out both the positive and negative aspects of the website. Additionally, our target was to present appropriate recommendations based on both well-known software design principles and user feedback to improve the usability of the mentioned application. 

The participant group for the experiment can be divided into two types- the authors who used and tested the system on their own, and the survey participants who shared their own experiences while using the software. 

\subsection{Participant Group I}

The authors followed a common pattern to navigate through the website. We checked out each header section and the links inside those that direct to different web pages the website consists of. For each web page, we tested the functionality it provides. We filled up the forms and input boxes where needed, and studied the information and instructions shared by the system admins. While going through the system, we specifically looked for potential information gaps, technical and visual disturbance as well as performance compromise.

\subsection{Participant Group II}

After preparing a primary overview of the system's usability, we created a questionnaire survey to distribute among the mass public to gather more data on the user experience. The questionnaire contains 4 major sections in it which are as follows: Basic participant information, User interface, instructions, and technical feedback, Speed and performance feedback, Contact, and overall feedback. The detailed questionnaire can be found here \footnote{\url{https://forms.gle/6oEvZbymMfF7uzqq5}}. Based on the survey response, we validated our primary findings and found some new issues that we initially missed out on. Finally, we propose recommendations based on our overall findings from our experimental methods.