\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{soul}

% \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Custom Commands
\newcommand{\ie}{\textit{i.e.},\ }
\newcommand{\eg}{\textit{e.g.},\ }
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{{\em etc.}}

\newcommand{\latif}[1]{\textcolor{blue}{\textit{#1}}}
\newcommand{\joanna}[1]{\textcolor{red}{\textit{#1}}}
\usepackage{enumitem}           % for numbered enumerations and margins
\usepackage[most]{tcolorbox}
\usepackage[parfill]{parskip}

\newcommand{\complexity}[1]{$\mathcal{O}(#1)$}


\tcbset{
  parskip/.style={
    before={\par\pagebreak[0]\parindent=0pt},
    after={\parfillskip=0pt\par},
  },
}
\newtcolorbox{resultbox}[1][]{%
    colback=black!5,
    colframe=black!5,
    notitle,
    sharp corners,
    borderline west={2pt}{0pt}{red!80!black},
    enhanced,
    breakable,
    boxsep=0pt,
    left=8pt,right=2pt,top=2pt,bottom=2pt,
    }
\newcommand{\rques}[1]{  
\begin{tcolorbox}[enhanced jigsaw,drop shadow=black!50!white,colback=white,left=2pt,right=2pt,top=2pt,bottom=2pt]
#1
\end{tcolorbox}
}

\pagenumbering{arabic}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
%*************************************************************
% BEGIN CUSTOMIZATIONS FOR MINTED PACKAGE                    *
%*************************************************************
% http://tug.ctan.org/macros/latex/contrib/minted/minted.pdf *
%*************************************************************
\usemintedstyle{tango}
\newminted{python}{frame=single,linenos,numbersep=3pt,fontsize=\scriptsize,xleftmargin=7pt}
\definecolor{codebg}{rgb}{0.99,0.99,0.99}
\definecolor{hiliteColor}{rgb}{1,0.92549019607,0.6}
\definecolor{tainted}{rgb}{0,1,1}
\newcommand{\highlight}[1]{\colorbox{hiliteColor}{#1}}
\DeclareRobustCommand{\hlcyan}[1]{{\sethlcolor{tainted}\hl{#1}}}
\DeclareRobustCommand{\hlred}[1]{{\sethlcolor{red!25}\hl{#1}}}
\setlength\fboxsep{0.5pt}
\newcommand{\PythonCode}[3]{%
\inputminted[%
  highlightlines={#2},
  highlightcolor=hiliteColor,
  escapeinside=||,
  framerule=0.5pt,
  bgcolor=white,
  numbersep=2pt,
  framesep=15pt,
  firstnumber={#3}
]{python}{#1}}



\newmintinline{java}{fontsize=\scriptsize}

\newminted[JavaSourceCode]{java}{
    labelposition=topline,
    frame=single,
    numbersep=2pt,
    fontsize=\scriptsize,
    xleftmargin=5pt,
    framerule=0.5pt,
    linenos, rulecolor=\color{gray!60}
}


% CSE 326 ISD Group B2 : 3 \\
% Roll: 1805112, 1805110, 1805115, 1805113, 1805092, 1805116

\begin{document}

\title{Usability Analysis of Bangladesh e-Passport Portal: A Study on Public Software Project}

\author{\IEEEauthorblockN{Md. Asif Haider, Anika Monir}
\IEEEauthorblockA{Department of Computer Science and Engineering
}
\IEEEauthorblockA{Bangladesh University of Engineering and Technology
}}


\maketitle
% \begingroup\renewcommand\thefootnote{\textsection}
% \footnotetext{These authors equally contributed to this work.}
% \endgroup
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}
Public software projects play a significant role in making the lives of the citizens of a country much easier by providing public services at a large scale. The E-passport portal is such a website with a huge number of clients based in the context of Bangladesh. Hence, studying the web application from a Software Engineering and System Design point of view is crucial, especially when there is a scope for improving user experience. In this study, we analyze the web application and its features based on public opinion and first-hand testing. Finally, we suggest spot-on recommendations to improve the project further.
\end{abstract}

\begin{IEEEkeywords}
% code generation, complexity, transformer, zero-shot prompting,  pre-trained model, GitHub copilot
public software projects, questionnaire survey, e-passport, user experience
\end{IEEEkeywords}

\input{Files/intro}

% \input{Files/background}
% \input{Files/rquestions}

\input{Files/methodology}
\input{Files/result}

\input{Files/discussion}

% \input{Files/threats}
% \input{Files/relatedwork}
% \input{Files/conclusion}

\bibliographystyle{IEEEtran}
\bibliography{reference}

\end{document}
